\LaTeX\ Author Guidelines for ICCV Proceedings

### 2021-03-10 chapters/5_experiments_intro.tex
Rewrite supplementary material and add proofs

\textbf{Grid-graphs from CNN predictions} -- We also evaluate the clustering methods on the task of neuron segmentation in EM image volumes using training data from the CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge}.
We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}\footnote{See Appendix \ref{sec:cremi_details} for all details about training and data augmentation.}. The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}. 
Clustering algorithms largely benefit from long-range edge connections in the grid-graph, in addition to direct-neighbors ones. However, empirically, we found that long-range affinities predicted by the CNN are also more noisy, and adding only 10\% of them (by random sampling) gave the best results.
% \TODO{long-range 10\%} 
% Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. Long-range connections are more noisy. 10\% represents a good compromise.
We divided the three CREMI training samples, consisting of $\sim$196 million voxels each, into five sub-blocks for a total of 15 clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}).

\textbf{3D-rag from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-rag} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.  We obtain them by first computing 2D supervoxels from the CNN predictions (using a watershed algorithm seeded at the maxima of the smoothed boundary distance transform) and then building a 3D region-adjacency graph, whose edge weights are given by the CNN affinities averaged over the boundaries of adjacent supervoxels.

@@

HCC-Complete & 0.9206 & 4.531 & \textbf{0.210} & 1330 \\
HC-Complete & 0.9211 & 4.536 & 0.211 & 1020 \\

@@

@@

HCC-Complete & 0.5564 & 2.220 & 0.254 & 89 \\

@@

        \hspace*{5em}

@@

\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:extended_results_cremi}, in Appendix.}. Although a lot of heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale up to the largest graph instances considered here. By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, apart from the \emph{CREMI-gridGraph} instances. Despite this, on graphs where a GT clustering is known, GAEC does not achieve the best ARAND scores (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}). 
% To better understand these empirical results, we now make the following important observation.
% This can also be observed in our experiments on synthetic graphs (Fig. ? and ?), where the clustering with minimum multicut energy become very different from the ground truth clustering when the flip noise parameter $\eta$ is increased.

\textbf{Size of growing clusters: Sum vs Avg linkage} --
In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.\ \ref{fig:intro_figure} and \ref{fig:dendrograms} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}. This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights. This will then start a ``chain reaction'' where only a single cluster is agglomerated at the time. 
% This \emph{flooding strategy} in the agglomeration is not observed with other linkage methods, e.g. Average, which grow clusters of similar sizes in parallel.
In the following, we will show how this unique \emph{flooding strategy} of the sum-linkage methods can be both an advantage or a disadvantage, depending on the type of clustering problem.

@@

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows that the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut formulation of \cite{beier2017multicut} (see details in Appendix) achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information. 
To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no

>>>>

\textbf{Grid-graphs from CNN predictions} -- We also evaluate the clustering methods on the task of neuron segmentation in EM image volumes using training data from the CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge}.
We train a 3D U-Net \cite{ronneberger2015u,cciccek20163d} using the same architecture as \cite{funke2018large} and predict long-and-short range affinities 
as described in \cite{lee2017superhuman}. The predicted affinities $a_e\in[0,1]$, which represent how likely it is for a pair of pixels to belong to the same neuron segment, are then mapped to signed edge weights $w_e=a_e-0.5$, resulting in a 3D grid-graph having a node for each pixel/voxel of the  image\footnote{To map affinities to signed weights, we also tested the \emph{logarithmic mapping} proposed in \cite{finkel2008enforcing,andres2012globally}, but it performed worse in our experiments.}. 
% \TODO{long-range 10\%} 
% Adding long-range connections to the graph is generally helpful, but when many of them carry repulsive weights. Long-range connections are more noisy. 10\% represents a good compromise.
We divided the three CREMI training samples, consisting of $\sim$196 million voxels each, into five sub-blocks for a total of 15 clustering problems (named \emph{CREMI-gridGraph} in Table~\ref{tab:datasets_and_energies}). See Appendix \ref{sec:cremi_details} for extended details about training, data augmentation, and how we remove tiny clusters after running \algname{} on the \emph{CREMI-gridGraph} clustering problems.

\textbf{3D-rag from CNN-predictions} -- Lastly, we use the predictions of our CNN model to generate three graph instances (one for each CREMI training sample, named \emph{CREMI-3D-rag} in Table~\ref{tab:datasets_and_energies}), which have very similar structure to the \emph{Knott-3D} and \emph{Fruit-Fly} instances.  We obtain these problems by using a pipeline that is very common in neuron segmentation: a watershed algorithm generates superpixels and from those a 3D region-adjacency graph is built, where edge weights are given by the CNN predictions averaged over the boundaries of adjacent superpixels (details in Appendix \ref{sec:cremi_details}). 
% them by first computing 2D supervoxels from the CNN predictions (using a watershed algorithm seeded at the maxima of the smoothed boundary distance transform) and then building a 3D region-adjacency graph, whose edge weights are given by the CNN affinities averaged over the boundaries of adjacent supervoxels.

@@

% HCC-Complete & 0.9206 & 4.531 & \textbf{0.210} & 1330 \\
HC-Complete & 0.9211 & 4.536 & \textbf{0.211} & 1020 \\

@@

        \vspace*{1em}

@@

% HCC-Complete & 0.5564 & 2.220 & 0.254 & 89 \\

@@

        % \hspace*{5em}
        \vspace*{1em}

@@

\textbf{Multicut objective values} -- In Table~\ref{tab:datasets_and_energies}, we report the values of the multicut objective associated to the clusterings obtained with different \algname{} algorithms\footnote{Objective values achieved by Single and Complete linkage methods are much worse compared to other algorithms and are reported in Table \ref{tab:all_multicut_energies}, in Appendix.}. Although a lot of heuristics were proposed to better optimize this objective \cite{beier2016efficient,beier2014cut,kernighan1970efficient}, these methods are out of the scope of this paper, since they do not scale up to the largest graph instances considered here. By looking at results in Table~\ref{tab:datasets_and_energies}, we observe that GAEC almost always achieves the lowest objective values, apart from the \emph{CREMI-gridGraph} instances. Despite this, on graphs where a GT clustering is known, GAEC does not achieve the best ARAND scores (see Tables~\ref{tab:scores_gridGraph} and \ref{tab:scores_3drag}). 
% To better understand these empirical results, we now make the following important observation.
% This can also be observed in our experiments on synthetic graphs (Fig. ? and ?), where the clustering with minimum multicut energy become very different from the ground truth clustering when the flip noise parameter $\eta$ is increased.

\textbf{Size of growing clusters: Sum vs Avg linkage} --
In all the studied clustering problems, we empirically observe that sum-linkage algorithms like GAEC tend to grow clusters one after the other, as shown in Fig.~\hyperref[fig:intro_figure]{\ref*{fig:intro_figure}d} and Fig.~\ref{fig:dendrograms} by the unique agglomeration order of GAEC\footnote{This \emph{flooding agglomeration-strategy} of GAEC was also observed in \cite{kardoostsolving}.}. This is intuitively explained by the  following: initially, many of the most attractive edge weights have very similar values; when the two nodes $u,v$ with the highest attraction are merged, there is a high chance that they will have a common neighboring node $t$ belonging to the same cluster; thus, the interaction between the merged nodes $uv$ and $t$ is likely assigned to the highest priority, because it is given by the sum of two highly attractive edge weights. This will then start a ``chain reaction'' where only a single cluster is agglomerated at the time. 
% This \emph{flooding strategy} in the agglomeration is not observed with other linkage methods, e.g. Average, which grow clusters of similar sizes in parallel.
In the following, we will show how this unique \emph{flooding strategy} of the sum-linkage methods can be both an advantage or a disadvantage, depending on the type of clustering problem.

@@

\textbf{Results on CREMI challenge} -- 
Table~\ref{tab:cremi_leaderboard} shows that the \emph{HCC-Avg} and \emph{HC-Avg} clustering algorithms achieve state-of-the-art performances on the CREMI challenge, when combined to the predictions of our CNN.
Most of the other entries (apart from \emph{LSI-Masks} \cite{bailoni2020proposal}) employ super-pixels based post-processing pipelines and cluster 3D-region-adjacency graphs. As we show in Table ~\ref{tab:scores_3drag}, using super-pixels considerably reduces the size of the clustering problem and, consequently, the post-processing time. 
However, our method operating directly on pixels (\emph{gridGraph+HCC-Avg}) achieves better performances than superpixel-based methods (\emph{3D-rag+HCC-Avg}) and does not require the parameter tuning necessary to obtain good super-pixels, which is usually highly dataset dependent.
The method \emph{3D-rag+LiftedMulticut} based on the lifted multicut formulation of \cite{beier2017multicut} achieves the best scores overall, but it takes into account different information through the lifted edge weights that also depend on additional raw-data and super-pixel shape information. 
To scale up our method operating on pixels, we divided each test-volume into four sub-blocks, and then combined the resulting clusterings by running the algorithms again on the combined graph.
% Note that the test volumes of the challenge contain several imaging artifacts that make segmentation particularly challenging.
% However: handcrafted and dataset dependent, performs better, no
